Rotation Periods in Low-Mass Binary Stars: The Impact of Tidal Torques

### 2018-11-14 Paper/sync.tex

- Consult Lurie's paper for CPL vs CTL (e.g. why not 3:2 population-> use CTL!) and for discussing sunsync population

- cite Matsen+2018 for "more than $50\%$ of thebinary period distribution will be imaged in about $85\%$ of the host stars" in paper
about detecting unresolved binaries in TESS

@@

@@

we can explain fast rotation observed in \citet{Meibom2007} to be due to tidal torques speeding up stellar Prots

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption.}%
    \label{fig:coupledExample}%
\end{figure}

@@

>>>>

- Consult Lurie's paper for CPL vs CTL (e.g. why not 3:2 population-> use CTL!) and for discussing sunsync population. stars prob not in 3:2 resonance since they likely dont have a fixed solid body shape as I assume, but perhaps in a decoupled core envelope model (bouvier?) envelope could get locked into resonance

- cite Matsen+2018 for "more than $50\%$ of the binary period distribution will be imaged in about $85\%$ of the host stars" in paper
about detecting unresolved binaries in TESS

@@

- lower left cluster in ProtPorb space in Lurie plot are likely BD or exoplanets according to Lurie

- compare results to Lurie section 4.4.2 discussion of dependence with eccentricity

- lurie finds that low mass ratio binaries are more likely to be subsync for Porb less than 10 days, makes sense since lower mass secondary means weaker tidal torques

- we can explain fast rotation observed in \citet{Meibom2007} to be due to tidal torques speeding up stellar Prots

@@

\section{The Rotational Equilibrium State} \label{sec:eq}

@@

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/lockedProtHist.pdf}
   \caption{Caption.}%
    \label{fig:lockedInteracting}%
\end{figure}
